\section{Recommendations}

\subsection{Regarding Error Handling}

You talk about it slightly in section 3 \emph{TCP and UDP differences}, when you mention that UDP does not guarantee the packets arrival nor the packets arriving in correct order.

Therefore i would recommend that you should read about how TCP does its error checking and error recovery. Guru99 has made an article\cite{guru_tcp_vs_udp} about this topic, where they compare the features of both UDP and TCP. 

I believe that your article will benefit from adding a subsection, that explains more in-depth, how the two protocols handles errors. It doesn't have to be a large section, simply write about a few pointers.

In addition to the Guru99 article, you could also take a look at an article written by GeeksforGeeks\cite{gfg_tcp_vs_udp}. This article explains how the error control in TCP is done with three simple techniques.

\subsection{Regarding Future Works}

In section 5 \emph{Future Work}, you talk about what you would have liked to investigate and experimented on, if you were to elaborate further on the subject. An addition to these ambitions could be to test the performance difference on the platform OpenVPN. 

OpenVPN is a virtual private network system. This platform allows you to implement techniques, to create secure point-to-point or site-to-site connections and much more. A couple of students at the University of Mauritius have made an article\cite{research_gate_tcp_vs_udp} on this subject, which I think would interest you and be a nice addition to your article.